{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation

### 2012-02-03 paper/paper.tex
removed duplicate 'of'
corrected subscript of relation
fixed typo

To define what noninterference means we need a notion of execution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq \text{SeqState} \times
\text{SeqState}$. One step execution for the multithreaded language $\leadsto_{seq}
\subseteq (\text{ConcState} \times \text{History}) \times (\text{ConcState} \times \text{History})$ is defined
by the rules in figure \ref{fig:multithreaded-execution}.

@@

The intuition is that the state $s$ evaluates according to a history $h$ to a final global memory $\mu$ iff there is a
sequence of concurrent executions that terminates (i.e. there are no active threads left) and has the
global memory $\mu$. $\leadsto_{conc}^*$ is the reflexive and transitive closure of of $\leadsto_{conc}$.

@@

They introduced the language $\lambda_{SEC}^{PAR}$ which supports higher-order functions, an
unbounded number of threads, synchronization (via join patterns), message passing and shared memory. Regardless of those realistic
features $\lambda_{SEC}^{PAR}$ is not intended to server as a user-lever programming language because its
syntax and type system is too awkward. Instead it is only used a model for studying information flow.

>>>>

To define what noninterference means we need a notion of execution. It is assumed
that we have a sequential execution relation $\leadsto_{seq} \subseteq \text{SeqState} \times
\text{SeqState}$. One step execution for the multithreaded language $\leadsto_{conc}
\subseteq (\text{ConcState} \times \text{History}) \times (\text{ConcState} \times \text{History})$ is defined
by the rules in figure \ref{fig:multithreaded-execution}.

@@

The intuition is that the state $s$ evaluates according to a history $h$ to a final global memory $\mu$ iff there is a
sequence of concurrent executions that terminates (i.e. there are no active threads left) and has the
global memory $\mu$. $\leadsto_{conc}^*$ is the reflexive and transitive closure of $\leadsto_{conc}$.

@@

They introduced the language $\lambda_{SEC}^{PAR}$ which supports higher-order functions, an
unbounded number of threads, synchronization (via join patterns), message passing and shared memory. Regardless of those realistic
features $\lambda_{SEC}^{PAR}$ is not intended to server as a user-level programming language because its
syntax and type system is too awkward. Instead it is only used a model for studying information flow.
